Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-05-21 Paper/gammaRays.tex
Plot \[Kappa]CDFPlot from sample16IA

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{kappaDistributionHistogram}
                \label{fig:kappaDistributionHistogram}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{kappaDistributionCDF}
                \label{fig:kappaDistributionCDF}
        \end{subfigure}
        \caption{The histogram and the CDF of the stretching factors sample produced by our model (blue). The sample contains $600$ points. The gray curve is an empirical CDF of the observed sample (4 points).}
        \label{fig:kappaDistribution}
\end{figure}

>>>>

\begin{figure}
	\hspace*{\fill}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{kappaDistributionHistogram}
		\label{fig:kappaDistributionHistogram}
		\caption{Histogram (blue) obtained from the model. Bar lines (black) show observed stretching factors.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{kappaDistributionCDF}
		\label{fig:kappaDistributionCDF}
		\caption{CDF (blue) obtained from the model. Gray curve and bar lines show observed stretching factors.}
	\end{subfigure}
	\hspace*{\fill}
	\caption{Stretching factors histogram and CDF produced by our model. The sample contains $16$ inaccurate bursts.}
	\label{fig:kappaDistribution}
\end{figure}
